---
title: "613HW2"
author: "Ting Yi Chuang"
date: "2024-01-23"
output: html_document
---

```{r}
library(tidyverse)     
library(dplyr)
```
4) Write an if- else if- else sequence of commands that will output the following
statements and appropriate output; If a value is divisible by 3 and 5 the output
statement is "divisible by Three and Five", If a value is divisible by 3 and 4, 
the output statement is "divisible by Three and Four, If a value is a number that
does not fall into either category, the output statement should be  "neither".
Use your function to show output statements for values 16, 45, and 24.

```{r}
B <- function(y) {
  if (y %% 3 == 0 && y %% 5 == 0) {
    print("divisible by Three and Five")
  } else if (y %% 3 == 0 && y %% 4 == 0) {
    print("divisible by Three and Four")
  } else {
    print("neither")
  }
}

B(20)
B(90)
B(48)
```

5) Use piping and a dplyr command show and use R code to produce the following modified mpg data table that contains only quantitative variables

Now use the “special loop coding chunk”, illustrated in class, to produce the variance for all variables of the modified data table.

```{r}
mpg_quantitativevariables <- mpg %>% 
  select_if(is.numeric)

output <- vector("double", ncol(mpg_quantitativevariables))  
for (i in seq_along(mpg_quantitativevariables)) {
  output[[i]] <- var(mpg_quantitativevariables[[i]]) 
}

output
```

6) Construct a for loop (as illustrated in the notes) that will produce the difference between the cube and the square for each prime number between 10 and 30.  (There are 6 answers. The first answer is 1210, your for loop coding should produce the other five answers)

```{r}
prime <- function(num) {
  if (num == 2) {
    return(TRUE)
  }
  if (num < 2 || num %% 2 == 0) {
    return(FALSE)
  }
  for (i in 3:sqrt(num)) {
    if (num %% i == 0) {
      return(FALSE)
    }
  }
  return(TRUE)
}

for (number in 10:30) {
  if (prime(number)) {
    difference <- number^3 - number^2
    print(difference)
  }
}
```
