---
title: "613HW4"
author: "Ting Yi Chuang"
date: "2024-02-06"
output: html_document
---

1)

a) Use the R function nrow to confirm that the iris data frame has 150 rows. Then use and show R code that features a map function to confirm that the iris data frame has 150 rows.

```{r}
library(tidyverse)
nrow(iris)
glimpse(iris)
```

b) Each column of the iris data frame has a unique number of values or objects. For example, the column Sepal.Length has 150 values but 35 of them are unique. Use and show R code that features a map function to find the number of unique values or objects for each column of the iris data frame.

```{r}
library(purrr)

map(iris, ~length(unique(.)))
```

2) Use and show R code that features a nested loop that will produce the  5 by 3 matrix shown below.

```{r}
matrix1 = matrix(nrow=3, ncol=5) 
for(i in 1:nrow(matrix1))        #// Assigned a variable 'i' for each row
{
  for(j in 1:ncol(matrix1))      #// Assigned a variable 'j' for each column
  {
    matrix1[i,j] = j-i          
  }
}
print(matrix1)
```

3) Use and show R code that will produce a tibble that features 10 randomly generated values that are normally distributed, with means of -10, 0, 10 and 100 respectfully.  Run your code again, producing a second tibble, that confirms random values, hence the second table will not have the same values.

```{r}
tribble( ~mean, ~sd,  ~n,
        -10,       1,   10,
        0,      1,   10,
        10,      1,  10,
        100,     1,   10
        ) -> parameters
parameters

pmap(parameters, rnorm)
pmap(parameters, rnorm)
```

4) 

```{r}
X <- list(12, 14, 15, 18, 19, 22,10,18,18)
Mean <- list(16, 16, 16, 16, 16,16,16,16,16)
sd <- list(2, 2, 2, 2, 2,2,2,2,2)
```

a) In statistics, a z score indicates the standard deviation distance between the mean and a specific value of the data set. What formula is used to find a z score? Use and show R coding that features a map function to iteratively find z scores across the lists given above.

```{r}
pmap_dbl(list(X,Mean,sd), function(first, second, third) (first - second) / third)
```

b) The test statistic for a population mean is given by the formula ((X - mean)/s/sqrt(n)) Use and show R coding that features a map function to iteratively find test statistics for population means across the lists given above.

```{r}
n <- length(X)
map2(X, sd, ~(.x - Mean[[1]]) / (.y / sqrt(n)))
```

5)

```{r}
V = c(10,15,17,22,32,38,42)
```

a) Another purr package function is the keep( ) function. Research, explore, and use the keep( ) function to extract all number from the vector V given above that are less than 20

```{r}
 keep(V, ~ .x < 20)
```

b) Another purr package function is the discard( ) function. Research, explore, and use the discard( ) function to eliminate all numbers from the vector V given above that are less than 20

```{r}
discard(V, ~ .x < 20)
```

6)
Another purr package function is the safely( ) function. Research, explore, and apply the 
 safely( ) function  to the given vector below as illustrated.
 
```{r}
U <- list(10, 15, "mary", 22, 32, "james", 42)
map(U, safely(~ .x + 15))
```

In four or five sentences, explain the specific output for this problem and how the definition and the application of the safely( ) function is used.

- For the numerical elements of the list (10, 15, 22, 32, 42), the operation `.x + 15` succeeds, and the `result` element holds the result of this addition. The `error` element is `NULL` because no error occurred. Then, for the character strings in the list ("mary", "james"), the operation `.x + 15` is not valid, we cannot add a number to a string in R. Therefore, the `result` element is `NULL` for these elements, and the `error` element contains an error object describing the problem.



